Simple Macroeconomic Forecast Distributions

### 2023-12-13 presentation/presentation.tex
better naming of figures

\section{Results}
\begin{frame}{Scores }
%\textit{I'll make the figures, incl. legends, nicer and also remove (the reason for) the joke about the devoured overprediction}
    \begin{figure}
        \centering
        \includegraphics[width=0.95\textwidth]{figures/wis_cpigdp_new.pdf} 
        \label{fig:enter-label}
    \end{figure} 
\end{frame}

@@

\appendix
\beginbackup
\begin{frame}{Directional Errors - Scores}
\label{errorextraction}
\begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/wis_cpigdp_new_directional.pdf}
       %\caption{Coverage at the 50 and 80 percent level}
    \end{figure}
\end{frame}
\begin{frame}{Directional Errors - Coverage}
\begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/coverage_directional.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
    \end{figure}
\end{frame}

\begin{frame}{Expanding Window - Scores}
\label{extractionmethod}
\begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/wis_cpigdp_new_ew.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
    \end{figure}
\end{frame}
\begin{frame}{Expanding Window - Coverage}
\begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/coverage_ew.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
    \end{figure}
\end{frame}

>>>>

\section{Results}
\begin{frame}{Scores }
%\textit{I'll make the figures, incl. legends, nicer and also remove (the reason for) the joke about the devoured overprediction}
    \begin{figure}
        \centering
        \includegraphics[width=0.95\textwidth]{figures/wis_cpigdp.pdf} 
        \label{fig:enter-label}
    \end{figure} 
\end{frame}

@@

\appendix
\beginbackup
\begin{frame}{Directional Errors - Scores}
\label{errorextraction}
\begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/wis_cpigdp_directional.pdf}
       %\caption{Coverage at the 50 and 80 percent level}
    \end{figure}
\end{frame}
\begin{frame}{Directional Errors - Coverage}
\begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/coverage_directional.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
    \end{figure}
\end{frame}

\begin{frame}{Expanding Window - Scores}
\label{extractionmethod}
\begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/wis_cpigdp_expandingwindow.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
    \end{figure}
\end{frame}
\begin{frame}{Expanding Window - Coverage}
\begin{figure}
        \centering
        \includegraphics[width=0.9\textwidth]{figures/coverage_expandingwindow.pdf}
        %\caption{Coverage at the 50 and 80 percent level}
    \end{figure}
\end{frame}
